Black swans in ecological time series\\ Black swans in population dynamics\\ Heavy-tailed ecological time series\\ Black swans in ecological dynamics\\ Black swan ecological dynamics\\ \ldots

### 2014-11-06 text/supp.tex
Update priors captions in SOM

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=\textwidth]{../analysis/priors-gomp-base.pdf}
\caption{
TODO WILL ADD ALTERNATIVE $\nu$ PRIORS
  Probability density of the Bayesian priors for the Gompertz models. From left
  to right: (1) per capita growth rate at $\log$(abundance) = $0$: $\lambda \sim
  \mathrm{Normal}(0, 10^2)$; (2) scale parameter of t-distribution process
  noise: $\sigma \sim \mathrm{Half\mhyphen Cauchy} (0,
  2.5)$; (3) t-distribution degrees of freedom parameter: $\nu \sim
  \mathrm{Truncated\mhyphen Exponential}(0.01, \mathrm{min.} = 2)$; (4) AR1
  correlation coefficient of residuals: $\phi \sim \mathrm{Truncated \mhyphen
    Normal}(0, 1, \mathrm{min.} = -1, \mathrm{max.} = 1)$. Not shown is $b$,
  the density dependence parameter: $b \sim \mathrm{Uniform}(-1, 2)$.
}
  \label{fig:priors}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.27\textwidth]{../analysis/order-level-estimates.pdf}
\caption{
TODO WILL COMBINE WITH COEFFICIENT POSTERIORS IN MAIN TEXT FIG 4
  Taxonomic-order-level posterior estimates of probability that $\nu < 10$ from
  a beta regression multilevel model accounting for the effect of time-series
  length. Estimates are at the geometric mean of time series length across all
  the data (approximately 27 time steps). Colour shading refers to the
  taxonomic classes as indicated in Fig.~\ref{fig:nu-coefs} and
  Fig.~\ref{fig:correlates} (yellow for fishes, green for insects, purple for
  birds, and red for mammals). Short vertical line segments indicate median
  posterior estimates. Long dotted vertical line throughout the figure
  indicates the median expected Pr($\nu < 10$) from the prior distribution.
}
\label{fig:order-estimates}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.5\textwidth]{../analysis/stan-beta-correlates}
\caption{
TODO WILL MOVE TO MAIN TEXT WITH ORDER-LEVEL ESTIMATES
  Main effect posterior densities for potential correlates of heavy-tailed
  dynamics. The response variable was Pr($\nu < 10$) (approximately the
  probability of heavy tails). The beta regression model was fit on a logit
  scale with random intercepts for taxonomic class, taxonomic order, and
  species. All covariates were standardized by subtracting their mean and
  dividing by twice their standard deviation. Therefore, the coefficient values
  represent the expected effect of a change in two standard deviations of the
  raw input variable on the logit-transformed response variable.
}
    \label{fig:correlate-coefs}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.70\textwidth]{../analysis/perc-prob-increase-with-n}
\caption{
TODO WILL DELETE THIS
Expected percent increase in the probability of detecting heavy tails, Pr($\nu
< 10$), with an additional ten time steps of data. These values are based on
the curve shown in Fig.~\ref{fig:correlates}d, which is based on the
coefficient in Fig.~\ref{fig:correlate-coefs}. For example, we have about
a 12\% increased probability of observing heavy tails in a time series that has
60 time steps vs.\ a time series with 50 time steps.
}
\label{fig:perc-inc-p}
\end{center}
\end{figure}

>>>>

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.8\textwidth]{../analysis/priors-gomp-base.pdf}
\caption{
  Probability density of the Bayesian priors for the Gompertz models. From left to right and then top to bottom: (1) per capita growth rate at $\log$(abundance) = $0$: $\lambda \sim \mathrm{Normal}(0, 10^2)$; (2) scale parameter of t-distribution process noise: $\sigma \sim \mathrm{Half\mhyphen Cauchy} (0, 2.5)$; (3) t-distribution degrees of freedom parameter: $\nu \sim \mathrm{Truncated\mhyphen Exponential}(0.01, \mathrm{min.} = 2)$; (4) AR1 correlation coefficient of residuals: $\phi \sim \mathrm{Truncated \mhyphen Normal}(0, 1, \mathrm{min.} = -1, \mathrm{max.} = 1)$. Not shown is $b$, the density dependence parameter: $b \sim \mathrm{Uniform}(-1, 2)$. The $\nu$ panel also shows two alternative priors: a weaker prior $\nu \sim \mathrm{Truncated\mhyphen Exponential}(0.005, \mathrm{min.} = 2)$, and a stronger prior $\nu \sim \mathrm{Truncated\mhyphen Exponential}(0.02, \mathrm{min.} = 2)$.
}
  \label{fig:priors}
\end{center}
\end{figure}

@@

@@
